Crunching Large Graphs with Commodity Processors

### 2011-04-19 doc/hotpar2011/softxmt-hotpar2011.tex
eval: prefetches paragraph revised
rewrite some fig captions

%\documentclass{acm_proc_article-sp}
\documentclass[10pt,nocopyrightspace,preprint]{sigplanconf}
\usepackage{url}
\usepackage{fancyvrb}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{comment}
\usepackage[labelfont=bf,font=small,belowskip=-3pt,aboveskip=-5pt]{caption}
\usepackage[compact]{titlesec}
\usepackage{mdwlist}
\usepackage{units}

@@

\begin{figure}[t]
  \vspace{-.1in}
	\begin{center}
		\includegraphics[width=0.47\textwidth]{figures/multi-listwalk-totalconc-edited.pdf}
	\end{center}
	\caption{Throughput of listwalk versus total number of
          concurrent references offered by the cores. Data points for
          running 1 core are shown as circles, and data points for
          running 6 cores are shown as diamonds. 
%Notice that the throughput for a single core levels out at 10
%concurrent references. For 4 to 6 cores, the throughput levels off at
%around 36 references, which seems to be the most memory concurrency a
%processor can handle.
        }
	\label{fig:listwalk-totalconc}
\end{figure}

@@

We observe a gradual decrease in reference rate once the number of
concurrent references per core exceeds 10; we believe this is due to
later prefetches squashing earlier ones in the line fill buffers. In the real runtime we expect this effect will not exist, since prefetch will not be implemented with built-in non-temporal prefetch instructions.\todo{pull that sentence and replace with something about no-prefetch results}. We
also observe many points that do not follow the trend are below the max, and these results are repeatable. This effect is harder to explain, but we suspect it is
due to resource contention in the cores' pipelines once the memory
system is full of requests.

>>>>

%\documentclass{acm_proc_article-sp}
\documentclass[10pt,nocopyrightspace,preprint]{sigplanconf}
\usepackage{url}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{comment}
\usepackage[labelfont=bf,font=small,belowskip=-3pt,aboveskip=-5pt]{caption}
\usepackage[compact]{titlesec}
\usepackage{mdwlist}
\usepackage{units}

@@

\begin{figure}[t]
  \vspace{-.1in}
	\begin{center}
		\includegraphics[width=0.47\textwidth]{figures/multi-listwalk-totalconc-edited.pdf}
	\end{center}
	\caption{Pointer chasing throughput versus total number of
          concurrent references offered by the cores. Total concurrent references offered is \emph{number of lists per core * number of cores}.
%Notice that the throughput for a single core levels out at 10
%concurrent references. For 4 to 6 cores, the throughput levels off at
%around 36 references, which seems to be the most memory concurrency a
%processor can handle.
        }
	\label{fig:listwalk-totalconc}
\end{figure}

@@

We observe a gradual decrease in reference rate once the number of
concurrent references per core exceeds 10; we believe this is due to
later prefetches squashing earlier ones in the line fill buffers. In the multi-node runtime, \texttt{readIssue} will not be implemented with a prefetch instruction. The single-node coroutine library does depend on prefetches: other experiments show that without them, the overhead of context switches limits concurrency when there are more than two coroutines per core. Lastly, we observe repeatable data points that are off the trend and fall below the max. This effect is harder to explain, but we suspect it may be
due to resource contention in the cores' pipelines once the memory
system is full of requests.
